Estimating the replicability of psychology experiments after an initial failure to replicate

### 2024-08-09 manuscript/coverletter/collabra_response.tex
Mike's edits, some linking

\makelabels
\usepackage{todonotes}
\usepackage{varioref}
\usepackage{xr}
\externaldocument[paper-]{../revision}
\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage[backend=biber,style=apa,doi=false,url=false,hyperref=true,apamaxprtauth=30,uniquename=false]{biblatex}
\usepackage{framed}
\DeclareLanguageMapping{american}{american-apa}
%\bibliography{../draft0}
\newcommand{\citet}[1]{\textcite{#1}}
\newcommand{\citep}[1]{\parencite{#1}}

\newcommand{\theysaid}[1]{\begin{leftbar} \noindent 
		\textsl{ #1}\end{leftbar}}
\newcommand{\revised}[1]{\begin{quote}	#1 \end{quote}}

\usepackage{longtable,booktabs,array}
\usepackage{float}
\begin{document}
	\name{Veronica Boyce}
\signature{\vspace{-35pt} Veronica Boyce, \\ on behalf of the author team}

@@

@@

		I also address some of reviewer 1's specific repo-related concerns below; I suspect many of them would have been ameliorated had the reviewer been able to download the repo.

@@

		\theysaid{Reviewer 1}

		\theysaid{The authors report the result of replication studies performed as part of an educational project. The results vary – some are relatively similar, of clear null replications, but others show a surprising amount of variability, possibly due to time and resource constraints, or a lack of experience. The main research question is what the probability is that failed studies can be rescued. The authors suggest this probability is rather low, but I think the current study does not really allow such generalizable conclusions. As Many Labs 5, the set of studies is not representative of the population. I have a number of observations that will hopefully help to improve the manuscript.}

		\theysaid{Data needs to be shared in a reproducible manner}
		\theysaid{Regrettably I could not download the files from github – some filenames that have been uploaded are too long, and both cloning the repo as downloading at a zip file give errors (on my windows machine). }

		We are sorry this error occurred, and that reviewer 1 didn't realize the files could be downloaded directly from the OSF copy (linked in the paper).  as the inability of reviewer 1 seems to have resulted in misunderstandings about the usability of files in the repo (which are much more understandable when opened on a computer).

		From googling, we believe this to be a windows issue, and to prevent this problem for future users we have added a note at the top of the README directing readers for how to address or sidestep the problem, namely:

		\revised{Note: If you are a windows user and get an error about overly long file names, please see [this stackoverflow post](https://stackoverflow.com/questions/22575662/filename-too-long-in-git-for-windows) or [this github issue](https://github.com/desktop/desktop/issues/17882) for how to fix it. Alternatively, you can download a zip of the repo from [the osf copy](https://osf.io/cyk5w/files/github) by clicking "Download this folder".}

@@

		We think the structure is actually pretty clear, but we apologize that the README was not more detailed. We have rewritten the README to be much more explicit about how to reproduce the paper as well as what all the folders and files contain.

		See  https://github.com/langcog/251-rescue-projects/tree/main for the revised README.

@@

		As we now clarify in the updated README, these are archival copies of the reports (which were posted to Rpubs). From a cloned/downloaded copy of the repo, the html files can be opened in a browser to see the reports.

		% \revised{\begin{verbatim}
		 %		### First-replication-reports and Individual-rescue-reports
		 %		* archival copies of the reports from individual projects, in case the rpubs links break or are overwritten
		 %		* to view, download the repo and open the html files in a browser

		 %	\end{verbatim}}

@@

		This is in an eval=F section, and process.Rmd both runs and knits without access to the file. However, to avoid future confusions, we have made the google spreadsheet openly viewable.

@@

		The manuscript is written in an Rmd file that is reproducible. Each of the individual rescue projects was also written in a Rmd or qmd reproducible report (included in the individual project repos included in individual-rescue-projects/). We have now clarified this in the README.

	%	\revised{ \begin{verbatim}
	%		The overall manuscript can be reproduced by knitting manuscript/manuscript.Rmd
	%		* This file reads data from data/combined_data.csv and data/boyce_2023_data.csv
	%		* This file uses code/helper/parse_stats.R \end{verbatim}}

	%	\revised{\begin{verbatim}
	%			### First-replication-projects and Individual-rescue-projects
	%		* include the individual replication and rescue projects (aka github repos) respectively
	%		* the rescue projects repos have been checked and include data, code/reproducible report, and the materials to run the experiment\end{verbatim}}

@@

		%TODO bug students whose stuff wasn't all there

		\theysaid{Focus on the qualitative data}
		\theysaid{It is interesting to see the results of these projects, as they show the messiness of results when quality control is less strict than in other replication projects. In some ways, the current set of studies can be regarded as a lower bound of replication success under very challenging conditions. Moreover, the qualitative insights when describing the individual studies (which should be extended) is quite educational. For example, it shows the importance of sharing materials, and provides an impetus to require material sharing when a paper is published.}

		We agree that the frustration of original materials not being available or original instructions not being available is education and hopefully serves as an impetus for more sharing.

@@

		 %TODO extend the case study

		 We thank the reviewer for this idea. We have added brief mentions of the topics and outcomes of each of the studies. We disagree about the ordering, as some readers may be more interested in the bottom line overall results than the individual studies. To support the different tastes, we have added an overview of subsections at the beginning of results so that interested readers could skip to the casestudies if desired.

		 %TODO add mention of the casestudies existance

		\theysaid{Be careful with generalizations}
		\theysaid{In the conclusions the authors generalize beyond the context of students doing replications, to investigators doing replications. However, I do not believe this project allows for such generalizations.}

		This reviewer seems to strongly distinguish between students and investigators. Perhaps this is from a misconception of who we are talking about when we talk about students (perhaps due to differences in training in different areas). To clarify, these were replications done primarily by first year PhD students at an elite US institution. Many publications (including in top journals) are in fact done by PhD students, under the supervision of professors. We checked the google scholars of the rescuers here and 7/17 of them (40\%) already had peer-reviewed journal publications, in some cases multiple. These students are or will soon be publishing in the literature. We agree that they may not have extensive expertise, but we think they and thus their rescue projects are reasonably representative of work by early career researchers with limited resources.

@@

		The original replications were performed under limitations, such as time limits and online samples, which we acknowledge, but which we believe is common when early career researchers build on existing work.

		As for when original materials aren't available, when they aren't available, the replications are as close as they can be, which may be not very close. Replicators did what they could given the external constrain of unavailable materials.

		[TODO not really sure what to say here]

		\theysaid{Experimental design of replication studies}
		\theysaid{The authors state they attempted to adequately power studies, but they refer to trying to achieve 2.5 times the sample size in the original study (ignoring the sample size and effect size in the replication study). But there are no details on what the original effect sizes were and how much power the replication studies had. There is only a mention of sample sizes, not of effect sizes. We only learn much later that several of the first replication studies had substantial challenges in recruiting sufficient participants, and had smaller sample sizes than the originals.}

		[TODO not sure what to do here]

		\theysaid{Subjective replication probability is unclear}
		\theysaid{The subjective replication probability coded as 0, 0.25, 0.75 and 1 is extremely confusing. It should be dropped.}

		We disagree. This coding was used in the paper this is follow-up to (https://royalsocietypublishing.org/doi/full/10.1098/rsos.231240) because it was the coding done at the time of (most) of the original replications.

		There are many metrics for what counts as a successful replication, but many of them depend on a key-statistic. As discussed in Hawkins et al 2018 (https://journals.sagepub.com/doi/full/10.1177/2515245917740427) and Boyce et al 2023 (https://royalsocietypublishing.org/doi/full/10.1098/rsos.231240), original papers often report a number of effects, and it is not always clear which one is the most key. Additionally, often the pattern of interest is dependent on multiple numeric effects (ex. two main effects and their interaction). Thus we think the holistic, subjective assessment of whether or not a study replicated is important, although we also do analyze the key effect as well.

@@

		As we write the in the methods section, ``Each project was rated on the basis of subjective replication success (on a 0--1 scale) by both MCF and one of VB and BP.
		We thought about replication in terms of general match in key study results (direction, magnitude, and significance), rather than focusing on any singular numeric result or significance cut-off.''

@@

		Whether a replication is statistically significant in the same direction as the original is one metric that is sometimes used as a measure of replicability, but as TODO CITE SOME PEOPLE SAYING THIS IS DUMB. Patil 2016, Simonsohn 2015, ANdrews and Kasy 2019 are potential cites here!

@@

		The effect sizes shown are SMDs, but in order to show everything on the same scale, we had to force everything onto that scale, even if it required a lot of conversions requiring approximations. For assessing individual studies it makes more sense to look at their raw results, rather the converted results.

		\theysaid{Statistical analysis}
		\theysaid{Upon first read I was not too enthusiastic about using a replication metric that incorporated heterogeneity. It seems a weird choice to treat unknown variability across studies as statistical uncertainty. Surely, in the end a replication study should mean that we observe the same effect size, and that we understand the topic sufficiently to observe a similar effect repeatedly. However, Figure 1 convinced me that in this context something else needs to be done, as the variability is simple huge. In part this must be due to the students doing the replications. I wonder if the authors redid all analyses and checked for mistakes. Some differences are just too large. We also know from the published literature that there is fraud in student projects, and I wonder if this has been checked.}

		We are fairly confident that there is not fraud as a) committing fraud would have been strictly more work than not and b) students had no incentive to commit fraud. During the class, students submitted their projects for a number of checkpoints. Thus, we know that students had working implementations of the studies because the TAs went through every experiment and gave feedback. Additionally, students had to have working code that ran on their pilot data before they were approved for data collection. We also know that the students ran studies on the class Prolific account because we can see how many participants were recruited and paid for each study. Thus, we know data was collected. Students knew that their grades in no way depended on what results they got (i.e. whether the study replicated), so had no incentive to change the data they had collected.

		Finally, don't you think that if students were going to commit fraud, they'd make the study work better? Even the studies that did rescue had smaller effect sizes than the original studies.

		We also have a larger sample of student replication studies conducted in previous years of the class, and these found a similar rate of replication as previous studies such as RP:P (see Boyce et al 2023).

@@

		I think there may be a misunderstanding here -- we aren't doing meta-analyses because we aren't interested in the aggregate effect size across the original and replications.

		When we discuss the "meta-analytic" mean of some studies that is because the measures of consistency we use (p-original) is between two things, so to compare more than two, some have to be pooled (which does make use of meta-analysis to do the pooling to get an aggregate mean and spread). As described in Mathur and VanderWeele 2020 (https://rss.onlinelibrary.wiley.com/doi/full/10.1111/rssa.12572) which introduces the statistic of p-original, it uses the point estimate and standard error of the original compared to the average population effect size in the replications and standard error thereof. As they mention, the most common way to get the average population effect size is via a random effects meta analysis.

		\theysaid{ First, I do not like the addition of additional replications. No systematic search has been done, so these studies might differ in some ways, and bias the overal effect size estimate. These additional studies can be mentioned, but, we should also see meta-analytic effect sizes without these replications.This can easily be presented in a table with different columns.}

		As we are only interested in studies that are direct replications of the original, we think we got them. 
		%TODO how to navigate this s

		%TODO add
		We understand the concern about wanting to see just the replication and rescue, so we have added a column to TABLE TODO with this.

		We again note that there appears to be a confusion over what is presented as we never present meta-analytic effect sizes for the reasons discussed above.

@@

		 Again, it seems like there may be confusion here -- the "p-values" presented here are "p-original" which is p-value like in that it's a measure of how likely an estimate would be to be at least as extreme as observed given a "null" distribution. It is a measure of statistical (in-)consistency on the effect sizes, not a measure of how close to zero the effect sizes are.

@@

		We have too few datapoints to meaningfully estimate the heterogeneity from our data (Mathur and VanderWeele suggest using the calculated tau if there are 10 or more replications); however, we also know the heterogeneity is not 0, so our best option is to use an estimated measure of heterogeneity, as is done as a sensitivity analysis in Errington et al 2021 and Boyce et al 2023.

		\theysaid{Minor points}
		\theysaid{Why is the median p-orig value reported? What does this tell us? I think this part of section 3.2 can be deleted.}

@@

		We apologize for this oversight and have added to the caption short descriptions for these two as well as a cross reference to where the predictors are discussed at length in Boyce et al 2023.

		%TODO DO THIS 
		\theysaid{It is the open science collaborations, not consortium.}

		%TODO FIX
		Oops, thank you for bringing this to our attention, we have fixed it.

@@

		\theysaid{Signed, Daniel Lakens}

		\theysaid{Reviewer 2}

		\theysaid{Thanks for the opportunity to review this paper.}

		\theysaid{I believe this is a well-written paper, with an interesting question: Should investigators devote more time to continued replications?
		In the paper, the authors try to “rescue” papers after an original failure to replicate. They show that in their relatively small sample of 17 studies, 5 could be rescued, and the others couldn’t, suggesting that rescuing studies has a high failure rate.}

		\theysaid{I do believe this is an interesting finding, although not completely surprising: in a world in which it is already hard to replicate studies, it make sense that it is even harder to rescue an outcome after a failed replication attempt. But the effort of the authors shows this elegantly, and it also shows, maybe surprisingly to some, that studies actually can be rescued, despite failed replication attempts earlier. In the debates on these issues so far, a failed replication is sometimes presented as the end of the discussion, and indirectly this study shows that it doesn’t have to be. I think the data leave room for multiple sometimes seemingly contradictory conclusions: one could argue that we should be careful in spending our limited resources on trying to rescuing a study that was already unsuccessfully replicated, whereas another could say that the difficulty in finding the right subjects can sometimes affect results in such a way that we should be careful in taking the failed replication too seriously.}

		\theysaid{So in general, I think the findings are interesting, and I think the authors did a good job in writing this up. What I am less convinced about is how this should inform decisions on rescuing papers. What does the general picture (a large majority of studies could not be rescued) tell me as a researcher who is contemplating rescuing a particular study? Since I assume that the selection of studies to be potentially rescued won’t be random, I probably already have reasons why I want to rescue this study. Either I am involved in the issue (I may be one of the people believing the original effect, or I may be even one of the authors of the original study), or I have reasons to believe that something went wrong in the replication study. Or I could believe that if the effect were true, this would be so important to know that it is worth taking the relatively large risk of a failure.}

		\theysaid{What I am trying to say is that the decision to re-replicate is most likely determined by many factors. The fact that on average (so, when picking a to be rescued study randomly) this probability is slim, should in my opinion only be a relatively small part of this decision. To me, this doesn’t disqualify this study, but I think it would be useful if the authors would acknowledge this somehow when discussing the implications of their findings.}

		This point is well taken and we have expanded our discussion to acknowledge the larger space of factors and decisions at play with replications and rescues and the motivations to do them. 
		%TODO make not suck

		\theysaid{One minor issue:}
		\theysaid{In the description of Figure 1, it is said that “the first replication’s key effect was non-zero”. I would expect all effects to be non-zero, so that’s not really informative. I guess what the authors mean is that supported for the original effect was found in the replication, or something along these lines}

>>>>

%\makelabels
\usepackage{todonotes}
\usepackage{varioref}
\usepackage{xr}
\externaldocument[paper-]{../revision}
\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage[backend=biber,style=apa,doi=false,url=false,hyperref=true,apamaxprtauth=30,uniquename=false]{biblatex}
\usepackage{framed}
\DeclareLanguageMapping{american}{american-apa}
\newcommand{\citet}[1]{\textcite{#1}}
\newcommand{\citep}[1]{\parencite{#1}}

\usepackage{longtable,booktabs,array}
\usepackage{float}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\newcounter{section}

\newcommand{\section}[1]{
	\bigskip
	{\normalfont\Large\bfseries #1}}

\newcommand{\theysaid}[1]{\begin{leftbar} \noindent 
		\textsl{ #1}\end{leftbar}}

\newcommand{\revised}[1]{\begin{quote}	#1 \end{quote}}

\usepackage{hyperref}
\begin{document}
	\name{Veronica Boyce}
	\signature{\vspace{-35pt} Veronica Boyce, \\ on behalf of the author team}

@@

		We would like to reiterate our thanks both the editor and the reviewers for their thoughtful and prompt reviews. We hope that our changes to the manuscript and the documentation of our repository offer the necessary clarifications and nuance.

		\closing{Sincerely,}

	\section{Editor}

@@

	We also address reviewer 1's specific repository-related concerns more below; we suspect many of them would have been ameliorated had the reviewer been able to download the repository files (which, as noted below, are likely due to a known technical issue with github and Windows systems).

@@

	\section{Reviewer 1}

	% \theysaid{The authors report the result of replication studies performed as part of an educational project. The results vary – some are relatively similar, of clear null replications, but others show a surprising amount of variability, possibly due to time and resource constraints, or a lack of experience. The main research question is what the probability is that failed studies can be rescued. The authors suggest this probability is rather low, but I think the current study does not really allow such generalizable conclusions. As Many Labs 5, the set of studies is not representative of the population. I have a number of observations that will hopefully help to improve the manuscript.}

	% \theysaid{Data needs to be shared in a reproducible manner}
	\theysaid{Regrettably I could not download the files from github – some filenames that have been uploaded are too long, and both cloning the repo as downloading at a zip file give errors (on my windows machine). }

	We are sorry this error occurred, and that reviewer 1 didn't realize the files could be downloaded directly from the OSF copy (linked in the paper).  The inability of reviewer 1 to download and open the files seems to have resulted in misunderstandings about the usability of files in the repo, which are much more understandable when opened on a computer.

	From googling, we believe the long files names issue to be a Windows issue, and to prevent this problem for future users we have added a note at the top of the README directing readers for how to address or sidestep the problem, namely:

	\revised{Note: If you are a windows user and get an error about overly long file names, please see \href{https://stackoverflow.com/questions/22575662/filename-too-long-in-git-for-windows}{this stackoverflow post} or \href{https://github.com/desktop/desktop/issues/17882} {this github issue} for how to fix it. Alternatively, you can download a zip of the repo from \href{https://osf.io/cyk5w/files/github}{the osf copy} by clicking "Download this folder".}

	Hopefully this warning will prevent future difficulties with accessing the repository.

@@

	We think the folder structure is actually pretty clear (e.g., \texttt{first-replication-projects} directory contains the first replication projects), but we apologize that the README was not more detailed. We have rewritten the README to be much more explicit about how to reproduce the paper as well as what all the folders and files contain.

	See  \url{https://github.com/langcog/251-rescue-projects/tree/main} for the revised README.

@@

	As we now clarify in the updated README, these are archival copies of the reports, which were originally posted to the Rpubs sharing website. From a cloned/downloaded copy of the repo, the html files can be opened in any web browser to see the reports.

@@

	It is common in RMarkdown files to add sections for documentation that do not need to be run every time to reproduce the result. Such sections are often marked \texttt{eval=F} and they do not evaluate. The piece of code referenced above is in such a section. \texttt{process.Rmd} both runs and knits without access to the file. However, to avoid future confusions, we have made the google spreadsheet openly viewable.

@@

	We apologize for any confusion about organization, but the manuscript is indeed written in an Rmd file that is fully  reproducible and is available in the repository. Each of the individual rescue projects was also written in a Rmd or Qmd reproducible report (included in the individual project repositories that are included in \texttt{individual-rescue-projects/}). We have now clarified this in the README.

@@

	% \theysaid{Focus on the qualitative data}
	\theysaid{It is interesting to see the results of these projects, as they show the messiness of results when quality control is less strict than in other replication projects. In some ways, the current set of studies can be regarded as a lower bound of replication success under very challenging conditions. Moreover, the qualitative insights when describing the individual studies (which should be extended) is quite educational. For example, it shows the importance of sharing materials, and provides an impetus to require material sharing when a paper is published.}

	We agree that the frustration of original materials not being available or original instructions not being available is educational and hopefully serves as an impetus for more sharing.

@@

	%TODO update after MS is potentially revised

	We thank the reviewer for this idea. We have added an Appendix with brief descriptions of the topics and outcomes of each of the studies.

	We disagree, however, about the ordering of quantitative and qualitative results. The quantitative results come directly from our preregistration and so should go first. In addition, we expect many readers will be more interested in the ``bottom line'' results than in the individual studies.

	% \theysaid{Be careful with generalizations}
	\theysaid{In the conclusions the authors generalize beyond the context of students doing replications, to investigators doing replications. However, I do not believe this project allows for such generalizations.}

	We appreciate the cautionary note, but we disagree about the generalizations that can be made from student work. In particular, the source of the disagreement may be the strong distinction the reviewer makes between between students and investigators. Perhaps this distinction comes from a misconception of who we are talking about when we talk about ``students,'' perhaps due to geographic or national differences in research training.

	To clarify, the replication rescues we report were performed primarily by first-year PhD students at an elite US institution, with a few more senior PhD students as well. These students were supervised and their work was reviewed by senior PhD students with research methods expertise and by the faculty instructor of the course. This supervision arrangement intentionally mirrors how research is typically conducted, even down to the multiple presentations of their replication projects that students give to the class (mirroring review and discussion in lab meetings). We expect that the reviewer would agree that many publications are in fact produced in exactly this way -- by PhD students, under the supervision of professors.

	We checked the google scholar pages of the student rescuers who are authors on our paper; 7/17 of them (40\%) already had peer-reviewed journal publications during the course, several of which were first-authored. These students are -- or will soon be -- publishing in the literature. We agree that they may not have extensive expertise, but we think they -- and thus their rescue projects -- are reasonably representative of work by early career researchers with limited resources.

	Since ``student'' can bring to mind different populations for different people, we have clarified in our limitations section who the rescuers were and how we think this is likely to generalize to other early career researchers (i.e. many of the people conducting research) but may not generalize to experts.

@@

	We disagree with the reviewer's characterization of our replication studies. There were some limitations for the original replications, including time limits and online samples. We believe these limits are common when early career researchers build on existing work: They may be limited in what resources (time, money, access to populations) are available, and so what results are accessible to them is relevant.

	As for when original materials aren't available, we believe that this limitation characterizes a vast amount of the replication literature. Unfortunately, materials availability is a severe issue. The extent to which this limitation affected our work is exactly the same as the extent to which it affects other investigators in non-student samples. Thus, if anything we would expect that this characteristic \emph{increases} the generality of our findings.

	% \theysaid{Experimental design of replication studies}
	\theysaid{The authors state they attempted to adequately power studies, but they refer to trying to achieve 2.5 times the sample size in the original study (ignoring the sample size and effect size in the replication study). But there are no details on what the original effect sizes were and how much power the replication studies had. There is only a mention of sample sizes, not of effect sizes. We only learn much later that several of the first replication studies had substantial challenges in recruiting sufficient participants, and had smaller sample sizes than the originals.}

	The idea behind 2.5x sample size is that it gives the replication an 80\% chance of correctly rejecting the null hypothesis of an effect that the original was 33\% powered for (see \href{https://doi.org/10.1177/0956797614567341}{Simonsohn, 2015, Psych Science}). This standard has the convenience of being agnostic to the type of experiment and test being conducted (unlike calculating effect sizes or calculating power, which both can be difficult to compute for complex designs and for cases where original data are not available). Per the Simonsohn proposal, the 2.5x multiplier is a target for answering the question, ``is there an effect big enough that the original study could have reasonably detected it.''

	% \theysaid{Subjective replication probability is unclear}
	\theysaid{The subjective replication probability coded as 0, 0.25, 0.75 and 1 is extremely confusing. It should be dropped.}

	We apologize, but we are not sure what is confusing about a holistic, rating-based metric for replication success. Indeed, the Replication Project in Psychology (Open Science Collaboration, 2015) included in its outcomes a subjective replication score. The current coding scheme was used in the paper that the current paper builds on ( \href{https://royalsocietypublishing.org/doi/full/10.1098/rsos.231240}{Boyce et al 2023}) because it was the coding done at the time of (most of) the original replications.

	There are many statistical metrics for what counts as a successful replication, including methods such as confidence interval overlap or the methods that we use in our quantitative results (e.g. p-original). The key issue with these measures is that they depend on the selection of a single key statistic for compariosn. As discussed in \href{https://journals.sagepub.com/doi/full/10.1177/2515245917740427}{Hawkins et al 2018} and Boyce et al 2023, original papers often report a number of effects, and it is not always clear which one is the most key. Additionally, often the theoretical pattern of interest -- as indicated by the authors -- is dependent on multiple numeric effects (ex. two main effects and their interaction). Thus, although we also analyze a key effect as well, we think the holistic, subjective assessment of whether or not a study replicated is an important part of our analysis.

	Finally, analysis of subjective replication ratings is one of our pre-registered analyses and so we do not believe it is appropriate to omit it.

@@

	We don't think this is a fair characterization of our rating scheme (which we have used in prior work, as discussed above).

	As we wrote the in the methods section, ``Each project was rated on the basis of subjective replication success (on a 0--1 scale) by both MCF and one of VB and BP.
	We thought about replication in terms of general match in key study results (direction, magnitude, and significance), rather than focusing on any singular numeric result or significance cut-off.''

@@

	Whether a replication is statistically significant in the same direction as the original is one metric that is sometimes used as a measure of replicability, but, as noted by \href{https://journals.sagepub.com/doi/10.1177/1745691616646366}{Patil et al 2016}, it isn't a very good one: one study may have an effect size very similar to another but one might be p < .05 and the other might be p > .05.

@@

	Regarding Figure 1, the effect sizes shown are standardized mean differences (SMD; Cohen's $d$). In order to show effects on the same graph, we had to coerce all the numbers to be SMDs, even if this conversion required approximations (as in the case of the Krauss paper, where the results are proportions). For assessing the statistical significance of individual studies it makes more sense to look at their raw results, rather the CIs in Figure 1, which are approximately correct but not the best basis for inference.

	% \theysaid{Statistical analysis}
	\theysaid{Upon first read I was not too enthusiastic about using a replication metric that incorporated heterogeneity. It seems a weird choice to treat unknown variability across studies as statistical uncertainty. Surely, in the end a replication study should mean that we observe the same effect size, and that we understand the topic sufficiently to observe a similar effect repeatedly. However, Figure 1 convinced me that in this context something else needs to be done, as the variability is simple huge. In part this must be due to the students doing the replications. I wonder if the authors redid all analyses and checked for mistakes. Some differences are just too large. We also know from the published literature that there is fraud in student projects, and I wonder if this has been checked.}

	We note that the heterogeneity metric has been used frequently to quantify variation in replication success, notably in \href{doi.org/10.1073/pnas.2403490121}{Holzmeister et al. (2024)}, which provides a framework for thinking about heterogeneity as stemming from population variation, design variation, and analytic variation.

	Regarding other sources of heterogeneity, including error and fraud, we think these are relatively unlikely.  First, while we did not recode student analyses from scratch, teaching assistants reviewed student code several times, and remarked on stylistic issues and potential errors. Further, most analyses were quite straightforward.

	We are also quite confident that there is not fraud in our sample. Committing fraud would have been strictly more work than actually doing the work, and further, there was no incentive to do so. During the class, students submitted their projects for a number of checkpoints. Thus, we know that students had working implementations of the studies because the TAs went through every experiment and gave feedback. Additionally, students had to have working code that ran on their pilot data before they were approved for running the main data collection. We also know that the students ran studies on the class Prolific account because we can see how many participants were recruited and paid for each study. Thus, we know code was written, the experiment worked, and the data was collected. Students also knew that their grades in no way depended on what results they got (i.e. whether the study replicated), so had no incentive to change the data they had collected.

	Finally, don't you think that if students were going to commit fraud, they'd make their study work \emph{better}? Even the studies that did rescue had smaller effect sizes than the original studies.

	Finally, regarding student error: in our prior work, we have a larger sample of 176 student replication studies, and these studies found a similar rate of replication as previous studies such as RP:P (see Boyce et al 2023). If error rates were substantially different, we'd expect lower replication.

@@

	We think there may be a misunderstanding here -- we aren't doing meta-analyses in order to aggregate effect size across the the original and replications.

	When we discuss the ``meta-analytic'' mean of some studies that is because the measures of consistency we use (p-original) is a measure of the consistency of two things. Thus, to compare more than two replications, some have to be pooled; we use meta-analysis to do the pooling to get an aggregate mean and standard error. As described in \href{https://rss.onlinelibrary.wiley.com/doi/full/10.1111/rssa.12572}{Mathur and VanderWeele 2020}, which introduces the p-original statistic, we uses the point estimate and standard error of the original compared to the average population effect size in the replications and standard error thereof. As they mention, the most common way to get the average population effect size is via a random effects meta analysis.

	\theysaid{First, I do not like the addition of additional replications. No systematic search has been done, so these studies might differ in some ways, and bias the overall effect size estimate. These additional studies can be mentioned, but, we should also see meta-analytic effect sizes without these replications.This can easily be presented in a table with different columns.}

	Students did search for direct replications of the studies, which if they are in the published literature are likely to be found. It is possible that there happen to be direct replications that aren't labeled as such that we could have missed, and of course, there could be unpublished or grey literature replications.

	We understand the concern about wanting to see just the replication and rescue, so we have added a column to Table 1 with this information.

	% New Table 1 shown below:

	% 	\begin{tabular}[t]{lrrrrr}
		% 		\toprule
		% 		\multicolumn{1}{c}{ } & \multicolumn{5}{c}{p-original comparing between} \\
		% 		\cmidrule(l{3pt}r{3pt}){2-6}
		% 		\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Original and} & \multicolumn{1}{c}{Rescue and} \\
		% 		\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-6}
		% 		Paper & All reps & 1st Rep and Rescue & Rescue & Non-rescue & Other reps\\
		% 		\midrule
		% 		Birch \& Bloom 2007 & 0.192 & 0.189 & 0.194 & 0.191 & 0.989\\
		% 		Child et al. 2018 & 0.669 & 0.669 & 0.641 & 0.858 & 0.778\\
		% 		Chou et al. 2016 & 0.055 & 0.055 & 0.101 & 0.005 & 0.231\\
		% 		Craig \& Richeson 2014 & 0.145 & 0.145 & 0.001 & 0.302 & 0.020\\
		% 		Gong et al. 2019 & 0.262 & 0.262 & 0.057 & 0.511 & 0.228\\
		% 		Haimovitz \& Dweck 2016 & 0.068 & 0.018 & 0.018 & 0.180 & 0.867\\
		% 		Hopkins et al. 2016 & 0.290 & 0.290 & 0.654 & 0.004 & 0.015\\
		% 		Jara-Ettinger et al. 2022 & 0.014 & 0.014 & 0.000 & 0.006 & 0.000\\
		% 		Krauss \& Wang 2003 & 0.271 & 0.271 & 0.519 & 0.139 & 0.311\\
		% 		Ngo et al. 2019 & 0.106 & 0.000 & 0.000 & 0.385 & 0.257\\
		% 		Paxton et al. 2012 & 0.011 & 0.011 & 0.005 & 0.023 & 0.649\\
		% 		Payne et al. 2008 & 0.023 & 0.071 & 0.031 & 0.079 & 0.895\\
		% 		Porter et al. 2016 & 0.370 & 0.370 & 0.905 & 0.002 & 0.003\\
		% 		Schechtman et al. 2010 & 0.712 & 0.712 & 0.654 & 0.770 & 0.877\\
		% 		Tarampi et al. 2016 & 0.000 & 0.000 & 0.000 & 0.000 & 0.145\\
		% 		Todd et al. 2016 & 0.062 & 0.100 & 0.124 & 0.058 & 0.778\\
		% 		Yeshurun \& Levy 2003 & 0.614 & 0.007 & 0.017 & 0.943 & 0.474\\
		% 		\bottomrule
		% 	\end{tabular}

	We again note that there appears to be a confusion over what is presented as we never present meta-analytic effect sizes for the reasons discussed above. We agree that such effect sizes wouldn't be easily interpretable.

@@

	Again, it seems like there may be confusion here -- the ``p-values'' presented here are ``p-original.'' p-original is a p-value, in that it's a measure of how likely an estimate would be to be at least as extreme as observed given a ``null'' distribution. But it is a measure of statistical (in-)consistency of the effect sizes, not a measure of how close to zero the effect sizes are. It does not correspond to a classical meta-analytic hypothesis test.

@@

	We have too few datapoints to meaningfully estimate the heterogeneity from our data (Mathur and VanderWeele 2020 suggest using the calculated tau if there are 10 or more replications); however, we also know the heterogeneity is not 0, so our best option is to use an estimated measure of heterogeneity, as is done as a sensitivity analysis in \href{https://elifesciences.org/articles/71601}{Errington et al 2021} and Boyce et al 2023.

	% \theysaid{Minor points}
	\theysaid{Why is the median p-orig value reported? What does this tell us? I think this part of section 3.2 can be deleted.}

@@

	We apologize for this oversight. We have changed these row names to ``Original authors at Stanford'' and 
	``Log number of trials''. We have also amended the caption to clarify the reason for Stanford being relevant as well as provide a reference to where the predictors are discussed at length in Boyce et al 2023.

	% The revised caption reads:

	% \revised{Correlations between an individual predictor and the subjective replication score of the rescue project. The first set of predictors were pre-registered based on the correlates used in Boyce et al. (2023). Original authors at Stanford refers to at the time of the first replication as this may mean the first replication was not independent. For details about how the predictors were coded, see the Methods section of Boyce et al. (2023). The last three predictors were added post-hoc.}

	\theysaid{It is the open science collaborations, not consortium.}

	Oops, thank you for bringing this to our attention, we have fixed it.

@@

	% \theysaid{Signed, Daniel Lakens}

	\section{Reviewer 2}

	% \theysaid{Thanks for the opportunity to review this paper.}

	% \theysaid{I believe this is a well-written paper, with an interesting question: Should investigators devote more time to continued replications?
		% In the paper, the authors try to “rescue” papers after an original failure to replicate. They show that in their relatively small sample of 17 studies, 5 could be rescued, and the others couldn’t, suggesting that rescuing studies has a high failure rate.}

	% \theysaid{I do believe this is an interesting finding, although not completely surprising: in a world in which it is already hard to replicate studies, it make sense that it is even harder to rescue an outcome after a failed replication attempt. But the effort of the authors shows this elegantly, and it also shows, maybe surprisingly to some, that studies actually can be rescued, despite failed replication attempts earlier. In the debates on these issues so far, a failed replication is sometimes presented as the end of the discussion, and indirectly this study shows that it doesn’t have to be. I think the data leave room for multiple sometimes seemingly contradictory conclusions: one could argue that we should be careful in spending our limited resources on trying to rescuing a study that was already unsuccessfully replicated, whereas another could say that the difficulty in finding the right subjects can sometimes affect results in such a way that we should be careful in taking the failed replication too seriously.}

	% \theysaid{So in general, I think the findings are interesting, and I think the authors did a good job in writing this up. What I am less convinced about is how this should inform decisions on rescuing papers. What does the general picture (a large majority of studies could not be rescued) tell me as a researcher who is contemplating rescuing a particular study? Since I assume that the selection of studies to be potentially rescued won’t be random, I probably already have reasons why I want to rescue this study. Either I am involved in the issue (I may be one of the people believing the original effect, or I may be even one of the authors of the original study), or I have reasons to believe that something went wrong in the replication study. Or I could believe that if the effect were true, this would be so important to know that it is worth taking the relatively large risk of a failure.}

	\theysaid{[...] the decision to re-replicate is most likely determined by many factors. The fact that on average (so, when picking a to be rescued study randomly) this probability is slim, should in my opinion only be a relatively small part of this decision. To me, this doesn’t disqualify this study, but I think it would be useful if the authors would acknowledge this somehow when discussing the implications of their findings.}

	This point is well taken and we have expanded our discussion to acknowledge the larger space of factors at play with replications and rescues and the motivations to do them.

	% \revised{Overall, the diminished and inconsistent effects we found in the rescues suggest that even if a re-replication ``works'', it may be difficult to build upon as follow-up studies will need large samples to detect small effects.
		% 	\newline

		% 	We have focused here on a narrow type of replication and rescue: that done by an early career researcher with the goal of establishing whether this is a result \emph{they} can build on. We acknowledge that this type of replication exists as part of a wider ecosystem of replications that have different properties and are done for different reasons.
		% 	\newline
